---
title: "Untitled"
author: "Qiutong CHEN"
date: "2025-05-04"
output: pdf_document
---

```{r setup, include=FALSE}
# Load required packages
library(haven)
library(dplyr)
library(modelsummary)
library(fastDummies)
library(quantreg)
library(hqreg)
library(car)
library(stargazer)
library(ggplot2)
library(forcats)

# Read the data
date3 <- read_dta("/Users/chenqiutong/Downloads/CGSS2017.dta")

# Select required variables
df1 <- date3 %>%
  select(a2, a31, a4, a7a, a45, a53, a10, a18,
         a53a, a561, a562, a563, a564, a565, a566, a567,
         a5698, a5699, a7b, a7c, a8a, a8b, a57b, a58,
         a59a, a59b, a59c, a59f, a59e, a59j, a59k,
         a89b, a89c, a89f, a89g, a89h, a90b, a90c, a90f, a90g, a90h,
         d36, c11, c12, a27b, a27d, c13, c14, c15, c16, c17, c18, c19, c110, c82, c20)

# Calculate age (using 2017 as the base year)
df1 <- df1 %>%
  mutate(age = 2017 - as.numeric(a31)) %>%
  filter(age <= 60)

# Filter valid income
df1 <- df1 %>%
  mutate(
    # Rename `a8b` to `annual_income`, handle special codes
    annual_income = ifelse(a8b %in% c(9999996, 9999997, 9999998, 9999999), NA, a8b),
    
    # Calculate log wage (only for positive income)
    log_wage = ifelse(annual_income > 0, log(annual_income), NA),
    
    # Winsorization at the top 1%
    log_wage = ifelse(
      log_wage > quantile(log_wage, 0.99, na.rm = TRUE),
      quantile(log_wage, 0.99, na.rm = TRUE),
      log_wage
    )
  ) %>%
  # Filter records where a8a is between 1000 and 9,000,000
  filter(a8a > 1000, a8a < 9000000) %>%
  filter(!is.na(log_wage))  # Drop missing values

# Process work status variable
df1 <- df1 %>%
  mutate(
    # Set values 98/99 as NA
    a59a = ifelse(a59a %in% c(98, 99), NA, a59a),
    # Convert to factor and assign labels
    a59a = factor(a59a,
                  levels = c(1:9),
                  labels = c("Boss/Partner", "Sole Proprietor", "Employed by Others",
                             "Laborer", "Casual Worker", "Self-employed (with salary)",
                             "Self-employed (without salary)", "Freelancer", "Other")),
    # Collapse the two self-employed categories into one
    a59a = fct_collapse(a59a,
                        "Self-employed" = c("Self-employed (with salary)", "Self-employed (without salary)")
  )

table(df1$a59a)

# Process a59f variable
df1 <- df1 %>%
  mutate(
    a59f = ifelse(a59f %in% c(98, 99), NA, a59f),
    a59f = factor(a59f,
                  levels = c(1:4),
                  labels = c("Manager", "Manage and be managed", "Only be managed", "No management")
  )
table(df1$a59f)

# Classify industry categories for a57b
df1 <- df1 %>%
  mutate(
    a57b_group = case_when(
      a57b == 1 ~ "Agriculture, Forestry, Animal Husbandry, and Fisheries",
      a57b %in% c(2, 3) ~ "Workers",
      a57b %in% c(4, 5) ~ "Business/Office Staff",
      a57b %in% c(6, 7) ~ "Managers",
      a57b %in% c(8:10) ~ "Technical Professionals",
      a57b %in% c(11, 12) ~ "Entrepreneurs/Sole Proprietors",
      a57b == 14 ~ "Students",
      TRUE ~ "Other/Missing"
    ),
    a57b_group = factor(a57b_group)
  )
table(df1$a57b)

# Convert education level a7a to an ordered factor
df1 <- df1 %>%
  mutate(edu_level = factor(a7a,
                            levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14"),
                            labels = c("No education", "Literacy classes", "Primary school", "Middle school", 
                                       "Vocational high school", "Regular high school", "Secondary specialized school", 
                                       "Technical school", "College diploma (adult HE)", "College diploma (regular HE)", 
                                       "Bachelor's (adult HE)", "Bachelor's (regular HE)", "Graduate and above", "Other"),
                            ordered = TRUE))

# Group education levels into categories
df1 <- df1 %>%
  mutate(edu_group = case_when(
    edu_level %in% c("No education", "Literacy classes") ~ "Primary_or_below",
    edu_level %in% c("Primary school", "Middle school") ~ "Junior_high",
    edu_level %in% c("Vocational high school", "Regular high school") ~ "High_school",
    edu_level %in% c("Secondary specialized school", "Technical school") ~ "Technical_secondary",
    edu_level %in% c("College diploma (adult HE)", "College diploma (regular HE)") ~ "College",
    edu_level %in% c("Bachelor's (adult HE)", "Bachelor's (regular HE)") ~ "Bachelor",
    edu_level == "Graduate and above" ~ "Graduate",
    TRUE ~ "Other"
  ))

# Specify factor levels and reference group
df1$edu_group <- factor(
  df1$edu_group,
  levels = c("Primary_or_below",
             "Junior_high",
             "High_school",
             "Technical_secondary",
             "College",
             "Bachelor",
             "Graduate",
             "Other"),
  ordered = FALSE
)

# Generate dummy variables, removing the first category (reference)
df1 <- dummy_cols(
  df1,
  select_columns = "edu_group",
  remove_first_dummy = TRUE,
  remove_selected_columns = FALSE
)

# Check factor levels
levels(df1$edu_group)
table(df1$edu_group)
print(names(df1)[grep("edu_group_", names(df1))])

# Process non-agricultural work years a59c, assign 0 to missing values
df1 <- df1 %>%
  mutate(
    a59c = case_when(
      a59c == 72 ~ 6,
      (is.na(a59c) | a59c %in% c(98, 99)) & !(a7c %in% c(0, 9997, 9998)) ~ 2017 - a7c,
      (is.na(a59c) | a59c %in% c(98, 99)) & (a7c %in% c(0, 9997, 9998)) ~ NA_real_,
      TRUE ~ a59c
    )
  )

# Process work type (a59e), work unit type (a59j), and ownership type (a59k)
df1 <- df1 %>%
  mutate(
    # a59e: unify 98, 99, and NA into "Missing"
    a59e = as.character(a59e),
    a59e = ifelse(a59e %in% c("98", "99") | is.na(a59e), "Missing", a59e),
    a59e = factor(a59e, levels = c("1", "2", "Missing"),
                  labels = c("Full-time", "Non-full-time", "Missing")),
    
    # a59j: similarly process
    a59j = as.character(a59j),
    a59j = ifelse(a59j %in% c("98", "99") | is.na(a59j), "Missing", a59j),
    a59j = factor(a59j, levels = c("1", "2", "3", "4", "5", "6", "7", "Missing"),
                  labels = c("Government", "Enterprise", "Public institution", "Social organization/Commune",
                             "No unit/self-employed", "Military", "Other", "Missing")),
    
    # a59k: similarly process
    a59k = as.character(a59k),
    a59k = ifelse(a59k %in% c("98", "99") | is.na(a59k), "Missing", a59k),
    a59k = factor(a59k, levels = c("1", "2", "3", "4", "5", "6", "Missing"),
                  labels = c("State-owned", "Collectively owned", "Private/Privately held",
                             "Hong Kong/Macau/Taiwan capital", "Foreign-owned", "Other", "Missing"))
  )

# Generate dummy variables (remove reference group)
df1 <- dummy_cols(df1, select_columns = c("a59e", "a59j", "a59k"),
                  remove_first_dummy = TRUE,
                  remove_selected_columns = FALSE)

# Merge categories with sample size < 100
df1 <- df1 %>%
  mutate(
    a59j = fct_lump_min(a59j, min = 200, other_level = "Other_merged"),
    a59k = fct_lump_min(a59k, min = 200, other_level = "Other_merged")
  )
table(df1$a59j)
table(df1$a59k)

df1 <- df1 %>%
  mutate(
    a59e = as.character(a59e),
    a59j = as.character(a59j),
    a59k = as.character(a59k),
    across(c(a59e, a59j, a59k), ~ifelse(.x == "Missing", "Missing", .x))
  )

library(fastDummies)
df_model <- df1 %>%
  dummy_cols(
    select_columns = c("a59e", "a59j", "a59k"),
    remove_first_dummy = TRUE,
    remove_selected_columns = TRUE
  ) %>%
  select(-contains("Missing"))  # Remove "Missing" dummies to avoid multicollinearity

# Calculate log wage a8b and winsorize at top 1%
df1 <- df1 %>%
  mutate(
    log_wage = log(a8b),
    log_wage = ifelse(log_wage > quantile(log_wage, 0.99, na.rm = TRUE),
                      quantile(log_wage, 0.99, na.rm = TRUE),
                      log_wage)
  ) %>%
  filter(!is.na(log_wage))

# Define custom merge function for parental education
merge_education <- function(x) {
  case_when(
    x %in% c(1, 2, 3) ~ "Low education (primary school or below)",
    x %in% c(4, 5, 6, 7, 8) ~ "Moderate education (middle/high school or technical school)",
    x %in% c(9, 10, 11, 12) ~ "Higher education (college/university)",
    x == 13 ~ "Graduate and above",
    x %in% c(14, 98, 99) ~ "Other/Missing"
  )
}

# Process father's education (A89b) and mother's education (A90b)
df1 <- df1 %>%
  mutate(
    father_edu = merge_education(a89b),
    mother_edu = merge_education(a90b),
    father_edu = factor(father_edu, 
                        levels = c("Low education (primary school or below)", 
                                   "Moderate education (middle/high school or technical school)", 
                                   "Higher education (college/university)", 
                                   "Graduate and above", 
                                   "Other/Missing"),
                        ordered = TRUE),
    mother_edu = factor(mother_edu, 
                        levels = c("Low education (primary school or below)", 
                                   "Moderate education (middle/high school or technical school)", 
                                   "Higher education (college/university)", 
                                   "Graduate and above", 
                                   "Other/Missing"),
                        ordered = TRUE)
  )

df1 <- df1 %>%
  mutate(
    father_edu = as.factor(father_edu),
    mother_edu = as.factor(mother_edu)
  )

str(df1$a89b)

# Create a gender dummy variable (assuming that 1 in a2 is male and the others are female)
df1 <- df1 %>%
  mutate(male = ifelse(a2 == 1, 1, 0))

df1 <- dummy_cols(
  df1,
  select_columns = "a57b_group",
  remove_first_dummy = TRUE,
  remove_selected_columns = FALSE
)

df1 <- dummy_cols(
  df1,
  select_columns = "a59a",
  remove_first_dummy = TRUE,
  remove_selected_columns = FALSE
)

df1 <- dummy_cols(
  df1,
  select_columns = "a59f",
  remove_first_dummy = TRUE,
  remove_selected_columns = FALSE
)

df1 <- df1 %>%
  mutate(
    father_edu = as.factor(father_edu),
    mother_edu = as.factor(mother_edu)
  )

df1 <- dummy_cols(
  df1,
  select_columns = c("father_edu", "mother_edu"),
  remove_first_dummy = TRUE,
  remove_selected_columns = FALSE
)
table(df1$a59a)
table(df1$a59f)
table(df1$father_edu)
table(df1$mother_edu)

df1 %>% 
  group_by(edu_group) %>% 
  summarise(mean_wage = mean(annual_income, na.rm = TRUE),
            prop_high_skill = mean(a59j == "Enterprise", na.rm = TRUE))

df1 <- df1 %>%
  mutate(
    hukou_type = factor(
      case_when(
        a18 == 1 ~ "rural_agricultural",
        a18 == 2 ~ "urban_non_agri",
        a18 == 3 ~ "rural_converted",
        a18 == 4 ~ "urban_converted",
        TRUE ~ "other"
      ),
      levels = c("rural_agricultural", "rural_converted", 
                 "urban_non_agri", "urban_converted")
    )
  ) %>%
  dummy_cols(select_columns = "hukou_type", remove_first_dummy = TRUE)
table(df1$a18, df1$hukou_type)

library(dplyr)
library(writexl)

# Tool function: Generate probability distribution table
library(dplyr)
library(writexl)

# Function to calculate probability distribution for a variable
get_distribution <- function(var, var_name) {
  tbl <- prop.table(table(var))
  df <- as.data.frame(tbl)
  colnames(df) <- c("Interval_or_Category", "Probability")
  df$Variable <- var_name
  df <- df[, c("Variable", "Interval_or_Category", "Probability")]
  return(df)
}

# 1. Process continuous variables: bin using cut(), then calculate proportions
df1$age_group <- cut(df1$age, breaks = seq(15, 60, by = 5), right = FALSE)
df1$income_group <- cut(df1$annual_income, breaks = 10)
df1$logwage_group <- cut(df1$log_wage, breaks = seq(6, 12, by = 0.2), right = FALSE)
df1$workexp_group <- cut(df1$a59c, breaks = seq(0, 40, by = 5), right = FALSE)
df1$gender <- ifelse(df1$male == 1, "Male", "Female")

# 2. Calculate probability distribution for each variable
dist_list <- list(
  get_distribution(df1$age_group, "Age"),
  get_distribution(df1$income_group, "Annual Income"),
  get_distribution(df1$logwage_group, "Log Income"),
  get_distribution(df1$gender, "Gender"),
  get_distribution(df1$workexp_group, "Work Experience"),
  get_distribution(df1$edu_group, "Education Level"),
  get_distribution(df1$a59a, "Employment Status"),
   get_distribution(df1$a59k, "Company Status"),
  get_distribution(df1$a59f, "Position Role"),
  get_distribution(df1$a57b_group, "Industry"),
  get_distribution(df1$hukou_type, "Hukou Type"),
  get_distribution(df1$father_edu, "Father's Education"),
  get_distribution(df1$mother_edu, "Mother's Education")
)

# 3. Combine all distributions into a single table
full_distribution <- bind_rows(dist_list)

# 4. Export to Excel (make sure 'writexl' package is installed)
write_xlsx(full_distribution, "CGSS2017_Variable_Probability_Distributions.xlsx")

#---------------------------------------------
# Quantile regression model
# The sample model here only selects some dummy variables:
# - For the nature of work (a59e), the a59e_Non.full.time dummy variable is used (reference group: Full-time)
# - For the type of work unit (a59j), the a59j_Enterprise is used (the reference group may be Government)
# - For the ownership of the unit (a59k), the a59k_State-owned is used (reference group: State-owned)
#qr_model <- rq(
#  log_wage ~ edu_group_High_school + edu_group_Technical_secondary + 
#edu_group_College + edu_group_Bachelor + edu_group_Graduate +
    #a59c + male + hukou_type_urban_non_agri + hukou_type_urban_converted  +
    #`a59e_Non-full-time` + a59j_Enterprise + `a59k_Foreign-owned`,
  #data = df1,
 # tau = c(0.25, 0.5, 0.75))

qr_model <- rq(
  log_wage ~ edu_group + a59c + male + hukou_type + a59a + a59f + a57b_group + father_edu + mother_edu,
  data = df1,
  tau = c(0.25, 0.5, 0.75)
)

summary(qr_model, se = "boot", R = 500)
library(broom)
library(dplyr)
library(ggplot2)

tidy_qr <- tidy(qr_model)
names(tidy_qr)

tidy_qr_sig <- tidy_qr %>% filter(conf.low * conf.high > 0)

ggplot(tidy_qr_sig, aes(x = tau, y = estimate, color = term)) +
  geom_line() +
  facet_wrap(~ term, scales = "free") +
  labs(title = "Trend of Bootstrap-Adjusted Coefficient Changes",
       subtitle = "Only significant variables (p < 0.05)")

library(car)

# Calculate VIF (needs linear model approximation)
lm_model <- lm(log_wage ~ edu_group + a59c + male + hukou_type + 
              a59a + a59f + a57b_group + father_edu + mother_edu, data = df1)
vif_values <- vif(lm_model)
print(vif_values)

# Visualizing the Correlation Matrix
cor_matrix <- cor(model.matrix(lm_model)[,-1])  # Excluding the intercept term
library(corrplot)
corrplot(cor_matrix, method = "number")

# This assumes the median regression model stored in qr_median (e.g. a model with tau=0.5)
pred_log_wage <- predict(qr_model, newdata = df1, tau = 0.5)
pred_wage <- exp(pred_log_wage)

residual_log <- df1$log_wage - pred_log_wage
df1 <- df1 %>%
  mutate(pred_log_wage = pred_log_wage,
         pred_wage = pred_wage,
         residual_log = residual_log)

# View some results
head(df1[, c("log_wage", "pred_log_wage", "pred_wage", "residual_log")])

```{r setup, include=FALSE}
# Define occupational prestige categories
high_prestige <- c(2, 6, 9)    # Executives, lawyers, police officers
medium_prestige <- c(5, 8, 10) # HR managers, nurses, junior high school teachers
low_prestige <- c(1, 3, 4, 7)  # Drivers, cleaners, hairdressers, car mechanics

# Create occupational prestige classification variables
df1 <- df1 %>%
  mutate(
    # High prestige occupation ties (strong ties: family/relatives = 1, friends = 2)
    high_prestige_strong = rowSums(across(
      .cols = c(c12, c16, c19),
      .fns = ~ .x %in% c(1, 2)
    )),
    
    # High prestige occupation ties (weak ties: acquaintances = 3)
    high_prestige_weak = rowSums(across(
      .cols = c(c12, c16, c19),
      .fns = ~ .x == 3)
    ),
    
    # Medium prestige occupation ties (strong ties)
    medium_prestige_strong = rowSums(across(
      .cols = c(c15, c18, c110),
      .fns = ~ .x %in% c(1, 2)
    )),
    
    # Medium prestige occupation ties (weak ties)
    medium_prestige_weak = rowSums(across(
      .cols = c(c15, c18, c110),
      .fns = ~ .x == 3
    )),
    
    # Low prestige occupation ties (strong ties)
    low_prestige_strong = rowSums(across(
      .cols = c(c11, c13, c14, c17),
      .fns = ~ .x %in% c(1, 2)
    )),
    
    # Low prestige occupation ties (weak ties)
    low_prestige_weak = rowSums(across(
      .cols = c(c11, c13, c14, c17),
      .fns = ~ .x == 3
    ))
  )

# Create composite network indicators
df1 <- df1 %>%
  mutate(
    # Total number of strong ties (across all prestige levels)
    total_strong_ties = high_prestige_strong + medium_prestige_strong + low_prestige_strong,
    
    # Total number of weak ties
    total_weak_ties = high_prestige_weak + medium_prestige_weak + low_prestige_weak,
    
    # High prestige network strength (considering tie strength weights)
    high_prestige_network = high_prestige_strong * 1 + high_prestige_weak * 0.5,
    
    # Network resource index (assigning higher weight to high prestige occupations)
    network_resource_index = (high_prestige_strong * 2 + high_prestige_weak * 1) +
                            (medium_prestige_strong * 1 + medium_prestige_weak * 0.5) +
                            (low_prestige_strong * 0.5 + low_prestige_weak * 0.25)
  )

# Calculate the mean and standard deviation of network_resource_index
mean_index <- mean(df1$network_resource_index, na.rm = TRUE)
sd_index <- sd(df1$network_resource_index, na.rm = TRUE)

# Construct a 95% confidence interval (roughly 95% of data under normal distribution)
lower_bound <- mean_index - 1.96 * sd_index
upper_bound <- mean_index + 1.96 * sd_index

# Calculate distribution quantiles
quantiles <- quantile(df_complete$network_resource_index, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE)
df_distribution_quantile <- df1 %>%
  mutate(interval = cut(network_resource_index, breaks = quantiles, include.lowest = TRUE)) %>%
  group_by(interval) %>%
  summarise(
    n = n(),
    probability = n() / nrow(df1)
  )
df_distribution_quantile

# R code example: create help type variable
df1 <- df1 %>%
  mutate(
    help_type = case_when(
      c82 == 1 | c82 == 2 ~ "informal",
      c82 == 3 | c82 == 4 | c82 == 5 ~ "formal",
      c82 %in% c(6,7) ~ "other",
      TRUE ~ NA_character_
    ),
    help_type = factor(help_type, levels = c("informal", "formal", "other"))
  )

# R code example: create network size variable
df1 <- df1 %>%
  mutate(
    contact_num = case_when(
      c20 == 1 ~ 2,
      c20 == 2 ~ 7,
      c20 == 3 ~ 14.5,
      c20 == 4 ~ 34.5,
      c20 == 5 ~ 74.5,
      c20 == 6 ~ 100,
      TRUE ~ NA_real_
    ),
    log_contact = log(contact_num + 1)  # Avoid taking log of zero
  )

# Remove all observations with missing values
df_complete <- na.omit(df1[, c("help_type","high_prestige_strong", 
                             "high_prestige_weak", "medium_prestige_strong",
                             "medium_prestige_weak","contact_num", "low_prestige_strong",
                             "low_prestige_weak", "network_resource_index")])

# Check remaining sample size
nrow(df_complete)  # If too few samples remain (e.g., <1000), consider alternative methods

# Quantile Regression Analysis Example
library(quantreg)
model11 <- lm(residual_log ~ help_type + contact_num + network_resource_index , data = df1)
summary(model11, se = "boot")
library(ggplot2)
library(broom)  # Extracting model results

# Extract coefficient, standard error, p-value
model_summary <- summary(model11, se = "boot")
coef_table <- as.data.frame(model_summary$coefficients)

# Arrange into a data frame
coef_df <- data.frame(
  term = rownames(coef_table),
  estimate = coef_table$Estimate,
  std.error = coef_table$`Std. Error`,
  p.value = coef_table$`Pr(>|t|)`,
  stringsAsFactors = FALSE)


```

